\def \phone{Phone}
\def \education{Education}
\def \bachelor{Bachelor in Computer Science}
\def \grade{grade overall}
\def \employment{Employment}
\def \february{Feb}
\def \present{Present}
\def \seniorsw{Senior Software Developer}
\def \picpayexplain{PicPay is a neobank that operates exclusively in Brazil. I'm part of the Open Banking business unit, and I have the following responsabilities:}
\def \picpaytopics{
  \item Design the internal platform that provides an API for data extraction from Open Banking ecosystem.
  \item Create backlog and help teams understand and implement the platform.
}
\def \picpayMainProjects{
  Designing the internal plataform for acessing data from Open Banking ecosystem.
}
\def \gbexplain{
Guiabolso was a mobile and web application for personal financial organization and a
financial product marketplace. I was part of the marketplace's team, and I had the
following responsibilities:}
\def \gbtopics{
\item Design technical solutions for new features of the marketplace.
\item Maintain back-office systems for personal loan and other financial products.
\item Implement new integrations with personal loan partners, banks, and investment companies.
\item Maintain the main financial product recommendation system.
\item Manage a team of three people.
}
\def \techUsed{Stack}
\def \mainly{mainly}
\def \mainProjects{Main projects}
\def \gbMainProjects{
Connection between Guiabolso's platform and various partner (like Digio
and Creditas); refactor of the platform’s product recommendation engine to use Decision
Model and Notation; integration between PicPay's and Guiabolso's personal loan platform.
}
\def \picpayBuy{PicPay bought Guiabolso in July 2021.}
\def \sw{Software Developer}
\def \softexpexplain{
Software Express Informática Ltda operated on the digital transaction market. Software
Express’s main software, SiTef, was a gateway between the POS (Point of Sale) and the
acquirer (companies that settle financial transactions). I was part of SiTef’s team, and I
had the following responsibilities:
}
\def \softextopics{
\item Analysis of the acquirer's documentation.
\item Implement integrations with the acquirers.
\item Run the integration test together with the acquirer's technical team.
\item Support the creation of new tools (both at a technical and functional level).
\item Support field troubleshooting.
}
\def \softexpMainProjects{
Integration with Global Payments, Elavon,
First Data, among others; refactor of various SiTef's configuration desktop applications;
implementation of a Postgre’s data backend that read local configuration files.
}
\def \mercurial{Mercurial version control}
\def \may{May}
\def \swIntern{Software Developer Intern}
\def \setopics{
\item Modify terminal (POS – Point of Sale) gateway applications.
\item Test, with the acquirer, the solution developed searching for issues.
\item Develop and maintain the SiTef's web server configurator.
}
\def \events{Events}
\def \courses{Courses}
\def \hours{hours}
\def \languages{Languages}
\def \englishLang{English - Advanced}
\def \portugueseLang{Portuguese - Native}
\def \standford{Standford University Online Course}
\def \december{Dec}
\def \relatedActivities{Related Activities}
\def \proatopic{
  \href{https://www.proa.org.br/en/instituto-proa-english/}{PROA}'s mentor since 2021.
  PROA is a non profit organization that aims to help families living in poverty.
  Every semester PROA selects a few hundred of young people for a free 6 month programming course.
  As a final project, the students form groups to make a presentation to employers about a web service implemented during the course.
  The mentor helps a group with that project.
}
